You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-25 paper/paper.tex
added human judgements bargraph

\section{Evaluation Metrics}
\begin{itemize}
  \item Describe the need for automatic evaluation metrics.
  \item Describe previously used evaluation metrics for paraphrase.
  \item Highlight problems with previous metrics when targeting a specific writing style.
  \item Propose new metrics.
\end{itemize}

>>>>

\section{Human Evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is innitially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgements of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
previous work has evaluated automatically generated paraphrases which target a specific style of writing \cite{chen11}.

While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it may also depend on style, since utterances
are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
is what portion of it's improvements are due to stylistic similarity or semantic equivelance.  For this reason, we were motivated perform
an evaluation based on human judgements of semantic adequacy, lexical dissimilarity and stylistic similarity.

For this purpose, we randomly sampled 100 lines from Romeo and Juliet, then two of the authors annotated each sentence and it's Shakesperean
translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overal quality.
The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.

\begin{figure}
  \begin{center}
    \includegraphics[width=4in]{figures/human_judgements.pdf}
  \end{center}
  \caption{Average human judgements evaluating semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality
    of Shakesperean paraphrase systems} 
  \label{human_judgements}
\end{figure}

%Argue why BLEU might capture writing style in addition to semantic adequacy
%Argue that we really want to seperate these two measures
%Present initial results from human evaluation (plot? - table?)
%Plot style vs. equivelance...?

\section{New Metrics Evaluating Writing Style}
